`r paste(params$species)` climatic and biotic velocities for `r paste(params$region)` (immature: `r paste(params$immature)`

### 2020-02-24 analysis/VOCC/3-vocc-dist.Rmd
add DO by its self to dvocc code, but haven't run it yet (only needed if dvocc stays in manuscript)

lower_change_t <- c(Inf, do_sd_choice*2) 
upper_change_t <- c(temp_sd_choice*2, do_sd_choice*2)

@@

dvocc_d <- make_vector_data(list(d, d),
  variable_names = c("temp", "do_est"),
  ssid = model_ssid,
  # start_time = 2013,
  # end_time = 2015,
  # skip_time = skip_time,
  input_cell_size = 2,
  scale_fac = scale_fac,
  min_dist = 0,
  delta_t_total = years_sampled,
  delta_t_step = 2,
  indices = indices,
  min_thresholds = lower_change_t,
  max_thresholds = upper_change_t,
  round_fact = 10
)

@@

gf0$dvocc <- dv_d$dvocc
```

@@

DO_values <- gf0 %>%
  rename(
    DO_vel = velocity,
    DO_dvocc = dvocc,
    DO_trend = trend_per_year,
    DO_grad = gradient,
    mean_DO = mean
  ) %>%
  select(x, y, DO_vel, DO_dvocc, DO_trend, DO_grad, mean_DO)

>>>>

lower_change_d <- c(do_sd_choice*2) 
upper_change_d <- c(do_sd_choice*2)

@@

dvocc_d <- make_vector_data(d,
  variable_names = c("do_est"),
  ssid = model_ssid,
  # start_time = 2013,
  # end_time = 2015,
  # skip_time = skip_time,
  input_cell_size = 2,
  scale_fac = scale_fac,
  min_dist = 0,
  delta_t_total = years_sampled,
  delta_t_step = 2,
  indices = indices,
  min_thresholds = lower_change_d,
  max_thresholds = upper_change_d,
  round_fact = 10
)

@@

gf0$dvocc <- dv_d$dvocc

lower_change_td <- c(Inf, do_sd_choice*2) 
upper_change_td <- c(temp_sd_choice*2, do_sd_choice*2)

dvocc_td <- make_vector_data(list(d, d),
  variable_names = c("temp", "do_est"),
  ssid = model_ssid,
  # start_time = 2013,
  # end_time = 2015,
  # skip_time = skip_time,
  input_cell_size = 2,
  scale_fac = scale_fac,
  min_dist = 0,
  delta_t_total = years_sampled,
  delta_t_step = 2,
  indices = indices,
  min_thresholds = lower_change_td,
  max_thresholds = upper_change_td,
  round_fact = 10
)

# glimpse(dvocc_d)
dvocc_td <- dvocc_td %>% mutate(dvocc = if_else(do_est.slope < 0, -km_per_decade, km_per_decade), trend= do_est.slope)

dvocc_td <- dvocc_td %>% mutate(dvocc = if_else(dvocc > (max_dist_all_years/ year_range)*10, 
  (max_dist_all_years/ year_range)*10, dvocc))
dvocc_td <- mutate(dvocc_td, dvocc = if_else(dvocc < -(max_dist_all_years / year_range)*10,
  -(max_dist_all_years / year_range)*10, dvocc))

dv_td <- dvocc_td %>% select(icell, x, y, dvocc) %>% unique()
# glimpse(dv_b)
# glimpse(gf0)

gf0$dvocc_both <- dv_td$dvocc
```

@@

DO_values <- gf0 %>%
  rename(
    DO_vel = velocity,
    DO_dvocc = dvocc,
    DO_trend = trend_per_year,
    DO_grad = gradient,
    mean_DO = mean
  ) %>%
  select(x, y, DO_vel, DO_dvocc, DO_trend, DO_grad, mean_DO, dvocc_both)
